Methods and Results

### 2022-10-04 ms.Rmd
Long dataset

  ###############
      # Variance in female fitness in harm and control treatment. Use lnCVR and lnVR (Nakagawa et al. 2015). On request of reviewer
  ################
   ## First, have a look at mean-variance relationships. Pretty strong relationship in both Treatment and Control group, as expected. 
    ggplot(data, aes(x = log(X_T), y = log(sd_T))) + 
      geom_point(size = 2, col = "black") + 
      geom_point(aes(x = log(X_C), y = log(sd_C)), col = "grey", size = 2) + 
      geom_abline() + 
      labs(x = "log Mean", y = "log SD") + theme_bw()

@@

# Exclude 4 studies that fail test. 3 effects are not defined in anycase
    data_cvr <- data %>% filter(geary_test == "pass")

@@

@@

>>>>

  ###############
      # Variance in female fitness in harm and control treatment. Use lnCVR and lnVR (Nakagawa et al. 2015). On request of reviewer
  ################
   ## First, have a look at mean-variance relationships. Pretty strong relationship in both Treatment and Control group, as expected. 
p1_1 <-   ggplot(data, aes(x = log(X_T), y = log(sd_T))) + 
      geom_point(size = 2, col = "black") + 
      geom_point(aes(x = log(X_C), y = log(sd_C)), col = "grey", size = 2) + 
      geom_abline() + 
      labs(x = "log Mean", y = "log SD") + theme_bw()

p2_2 <-ggplot(data, aes(x = X_T, y = sd_T)) + 
      geom_point(size = 2, col = "black") + 
      geom_point(aes(x = X_C, y = sd_C), col = "grey", size = 2) + 
      geom_abline() + 
      labs(x = "Mean", y = "SD") + theme_bw()

(p1_1 | p2_2) + plot_annotation(tag_levels = "A", tag_suffix = ")")

@@

# Exclude 4 studies that fail test. 3 effects are not defined in any case
    data_cvr <- data %>% filter(geary_test == "pass")

@@

  # We have a clear relationship bw SD and Mean, especially so on log scale, but raw scale not so much. We should check assumptions of lnCVR analysis

    # First, we need to reorganise the data in long format

    data_long <- data %>% pivot_longer(cols = c(14:19), values_to = "value") %>% 
                pivot_wider(names_from = grep(name, "sd"), values_from = value, ) %>% data.frame()

    data_long_mean <- data_long %>% filter(grepl("X_", name)) %>% mutate(obs = 1:n())
      data_long_sd <- data_long %>% filter(grepl("sd_", name)) %>% mutate(obs = 1:n()) %>% select(obs, name, value)
       data_long_n <- data_long %>% filter(grepl("N_", name)) %>% mutate(obs = 1:n()) %>% select(obs, name, value)

    # Now, merge data sets together.

       final_long1 <- left_join(data_long_mean, data_long_sd, by = "obs")
        final_long <- left_join(final_long1, data_long_n, by = "obs")

@@

  ###############
      # Final tables
  ################
